Smart Drill-Down

### 2014-11-28 TableSummarization/Paper/TableSummarization.tex
Switched to VLDB format
Several changes. Also added conclusion

%\documentclass{vldb}
\documentclass{sig-alternate}
%\documentclass[12pt,letterpaper]{article}
%\documentclass[12pt]{extreport}
%\documentstyle[amsmath,amsthm,amssymb,twocolumn]{article}
%\newcommand{\mytitle}{Evaluating the Crowd with Confidence}

\usepackage{amsmath}
\makeatletter
\let\@copyrightspace\relax
\makeatother
\pdfpagewidth=8.5in
\pdfpageheight=11in

\usepackage{enumitem}
\usepackage{times}
\usepackage{subfigure}
\let\proof\relax
\let\endproof\relax
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,color}
\usepackage{verbatim}
\usepackage{framed}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{framed}
\usepackage[normalem]{ulem}

@@

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}
      \setlength{\parsep}{2pt}
      \setlength{\topsep}{2pt}
      \setlength{\partopsep}{0pt}
    }
}
\newcommand{\stitle}[1]{\vspace{0.5em}\noindent\textbf{#1}}
\newcommand{\squishend}{\end{list}}
\newcommand{\eat}[1]{}
\newcommand{\papertext}[1]{#1}
\newcommand{\techreporttext}[1]{#1}

@@

\title{Smart Drill-Down: Interactive Summarization of Relational Tables}

\author{
Manas Joglekar\\Stanford University\\manasrj@stanford.edu
\and
Hector Garcia-Molina\\Stanford University\\hector@cs.stanford.edu
\and
Aditya Parameswaran\\University of Illinois\\adityagp@illinois.edu
}

@@

\maketitle

\begin{abstract}
In this paper we present {\em smart drill down},
a system for interactively exploring a relational table
to discover ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a $1000$ tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively drill down on an existing rule to
explore that part of the table.
We describe an
algorithm for finding the approximately optimal list of rules, and an optimized
sampling scheme for efficiently summarizing large tables. Finally, we
demonstrate the usefulness of smart drill down by performing experiments on
real datasets.
\end{abstract}

@@

\input{extensions}

@@

{\small 
\bibliographystyle{plain}
\bibliography{TableSummarization}
}
\techreporttext{\input{appendix}}

>>>>

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{enumitem}
\usepackage{times}
\usepackage{subfigure}
\let\proof\relax
\let\endproof\relax
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,color}
\usepackage{verbatim}
\usepackage{framed}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{framed}
\usepackage[normalem]{ulem}

@@

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}
      \setlength{\parsep}{2pt}
      \setlength{\topsep}{2pt}
      \setlength{\partopsep}{0pt}
    }
}
\newcommand{\stitle}[1]{\vspace{0.5em}\noindent\textbf{#1}}
\newcommand{\squishend}{\end{list}}
\newcommand{\eat}[1]{}
\newcommand{\papertext}[1]{#1}
\newcommand{\techreporttext}[1]{}

@@

@@

\title{Smart Drill-Down}
\numberofauthors{3} 
\author{
\alignauthor
Manas Joglekar\\
       \affaddr{Stanford University}\\
       \affaddr{353 Serra Mall}\\
	   \affaddr{Stanford, California 94305}\\
       \email{manasrj@stanford.edu}
\alignauthor
Hector Garcia-Molina\\
       \affaddr{Stanford University}\\
       \affaddr{353 Serra Mall}\\
	   \affaddr{Stanford, California 94305}\\
       \email{hector@cs.stanford.edu}
\alignauthor 
Aditya Parameswaran\\
       \affaddr{University of Illinois at Urbana-Champaign}\\
       \affaddr{Champaign, Illinois 61820}\\
       \email{adityagp@illinois.edu}
}
\maketitle

\begin{abstract}
In this paper we present {\em smart drill down},
an operator for interactively exploring a relational table
to discover ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a $1000$ tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively apply smart drill down on an existing rule to
explore that part of the table.
We describe an
algorithm for finding the approximately optimal list of rules to display when the user uses a smart drill down, and a dynamic sampling scheme for efficiently dealing with large tables. Finally, we
perform experiments on real datasets to demonstrate the usefulness of smart drill down and to study the performance of our algorithms.
\end{abstract}

@@

\techreporttext{\input{extensions}}

@@

\input{conc}

\bibliographystyle{abbrv}
\bibliography{TableSummarization}

% Example of an appendix; typically would start on a new page
%pagebreak

\techreporttext{\input{appendix}}

### 2014-11-28 TableSummarization/Paper/algorithms.tex
Several changes. Also added conclusion

\section{Smart Drill-Down Algorithms} \label{sec:algorithms}
We now describe online algorithms for implementing
the smart drill-down operator. We assume in this section that all columns are categorical (so numerical columns have been bucketized beforehand). We further discuss bucketization of numerical attributes in Section~\ref{sec:extensions} in the technical report~\cite{tr}.

@@

\noindent Problem~\ref{prob:optimal-subrule-list} with parameters $(T, W, k)$ can be reduced to Problem~\ref{prob:optimal-rule-list} as follows:
\begin{enumerate}
\item $[$Rule Drill-Down$]$ If the user clicked on rule $r$ in Problem~\ref{prob:optimal-subrule-list}, then we can conceptually make one pass through the table $T$ to filter for tuples covered by rule $r$, and store them in a temporary table $T_r$. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W, k)$.
\item $[$Star Drill-Down$]$ If the user clicked on a $\star$ in column $c$ of rule $r$, then we first filter table $T$ to get a smaller table $T_r$ consisting of tuples from $T$ that are covered by $r$. In addition, we change the weight function $W$ from Problem~\ref{prob:optimal-subrule-list} to a weight function $W^{\prime}$ such that : For any rule $r^{\prime}$, $W^{\prime}(r^{\prime}) = 0$ if $r^{\prime}$ has a $\star$ in column $c$, and $W^{\prime}(r^{\prime}) = W(r^{\prime})$ otherwise. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W^{\prime}, k)$.
\end{enumerate}

First, we show that the rules in the optimal list must effectively be ordered in decreasing order by weight. Note that the weight of a rule is independent of its $MCount$. The $MCount$ of a rule is the number of tuples that have been `assigned' to it, and each tuple assigned to rule $r$ contributes $W(r)$ to the total score. Thus if the rules are not in decreasing order by weight in a rule list $R$, then switching the order of rules in $R$ transfers some tuples from a lower weight rule to a higher weight rule, which can increase total score.

\begin{lemma}\label{lemma:rule-ordering}
Let $R$ be a rule-list. Let $R^{\prime}$ be the rule-list having the same rules as $R$, but ordered in descending order by weight. Then
$$\text{Score}(R^{\prime}) \geq \text{Score}(R)$$
\end{lemma}
Proofs of this lemma, as well as other proofs, can be found in the appendix of the technical report~\cite{tr}.

\noindent Thus it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, we can define Score for a set of rules as follows:

@@

This gives us a reduced version of Problem~\ref{prob:optimal-rule-list}: 
\begin{problem}\label{prob:optimal-rule-set}
Given a table $T$, a monotonic weight function $W$, and a number $k$, find the set $R$ of $k$ rules which maximizes Score($R$) as defined in Definition~\ref{def:set-score}.
\end{problem}

@@

\item In order to find the rule $r$ to add in each step, we need to measure the impact on Score for each $r$. This is done in several passes over the table, using ideas from the a priori algorithm~\cite{apriori} for frequent item-set mining. 
\squishend

In some cases, the dataset may still be too large for us to return a good rule set in
a reasonable time; in such cases, we may want to run our algorithm on a sample of the table
rather than the entire table. In Section~\ref{sec:sampling}, we describe a scheme 
for maintaining multiple samples in memory and using them to improve response 
time for different drill down operations performed by the user.

\subsection{Greedy Approximation Algorithm}\label{sec:greedy-approx}
\stitle{Submodularity:} We will now show that the Score function over sets of rules has a property called {\em submodularity}, giving us a greedy approximation algorithm for optimizing it. 
\begin{definition}
A function $f: 2^S \rightarrow \mathbb{R}$ for any set $S$ is said to be submodular if and only if, for every $s \in S$, and $A \subset B \subset S$ with $s \notin A$:
$$f(A \cup \left\lbrace s \right\rbrace) - f(A) \geq f(B \cup \left\lbrace s \right\rbrace) - f(B)$$
\end{definition}
Intuitively, this means that the marginal value of adding an element to a set $S$ cannot increase if we add it to a superset of $S$ instead. For monotonic non-negative submodular functions, the problem of finding the set of a given size with maximum value for the function can be found approximately in a greedy way.

@@

The parameter $m_w$ stands for \textit{Max Weight}. The parameter $m_w$ tells the algorithm to assume that all rules that get selected in the optimal solution are going to have weight $\leq m_w$. Thus, if $S_o$ denotes set of rules with maximum score, then as long as $m_w \geq \textrm{max}_{r \in S_o}W(r)$, Algorithm~\ref{algo:best-rule-set} is guaranteed to return $S_o$. On the other hand if $m_w < W(r)$ for some $r \in S_o$, then there is a chance that the set returned by Algorithm~\ref{algo:best-rule-set} does not contain $r$. Algorithm~\ref{algo:best-rule-set} runs faster for smaller values of $m_w$, and may only return a suboptimal result if $m_w < \textrm{max}_{r \in S_o}W(r)$. In practice, $\textrm{max}_{r \in S_o}W(r)$ is usually small. This is because as the size (and weight) of a rule increases, its Count falls rapidly. The Count tends to decrease exponentially with rule size, while Weight increases linearly for common weight functions (such as $W(r) = \text{Size}(r)$). Thus rules with high weight and size have very low count, and are unlikely to occur in the optimal solution set $S_o$. Our experiments in Section~\ref{sec:experiments} also show that the weights of rules in the optimal set tend to be small.

@@

In order to avoid counting too many rules, we use an idea from the {\em a priori} algorithm for frequent itemset mining~\cite{apriori}. We compute the best marginal rule over several passes, with the maximum number of passes equal to the maximum size of a rule. In the $j^{th}$ pass, we compute counts for rules of size $j$. To give an example, suppose we had three columns $c_1$, $c_2$, and $c_3$. In the first pass, we would compute the marginal values of all rules of size $1$. In the second pass, instead of finding marginal values for all size $2$ rules, we can use our knowledge of counts from the first pass to upper bound the potential counts of size $2$ rules, and be more selective about which rules to count in the second pass. For instance, suppose we know that the rule $(a, \star, \star)$ has a count of $1000$, while $(\star, b, \star)$ has a count of $100$. Then for any value $c$ in column $c_3$ we would know that the count of $(\star, b, c)$ is at most $100$ because it cannot exceed that of $(\star, b, \star)$. This implies that the maximum marginal value of any super-rule of $(\star, b, c)$ having weight $\leq m_w$ is at most $100m_w$. If the rule $(a, \star, \star)$ has a marginal value of $800$, then the marginal value of any super-rule of $(\star, b, \star)$ cannot possibly exceed that of $(a, \star, \star)$. Since our aim is to only find the highest marginal value rule, we can skip counting for all super-rules of $(\star, b, \star)$ for future passes.

@@

@@

MarginalValue($R$) $+=$ $W(R) - \text{min}(W(R), W(R_S))$
}
}
$C_o = C_n$

@@

$C = C \cup C_o$

@@

\subsection{Dynamic Sampling for Large Tables}\label{sec:sampling}
\subsubsection{Sampling Overview}
We now describe our sampling schemes for improving the running time of our algorithm on tables that are too large to fit in main memory. First in Section~\ref{sec:sample-using}, we motivate the need for sampling. Then we describe a component of our system, called the {\em SampleHandler}, which is responsible for creating and maintaining samples of the table in memory, subject to user specified memory constraints. The SampleHandler maintains multiple samples corresponding to different parts of the table, which can be used depending on which rule the user decides to expand next. Then in Section~\ref{sec:sampling_algorithms}, we describe ways to efficiently allocate memory to different samples, so as to maximize the probability that we can respond to the next user operation without accessing the hard disk. Finally, we mention some additional optimizations we can make, and heuristics for setting the minimum sample size required from the SampleHandler.

@@

At all points, the SampleHandler maintains a set of Samples in memory. For instance, it may keep a sample of tuples used to expand the first (trivial) rule, and another sample used to expand the rule last clicked on by the user. Each sample $s$ is an object with three attributes: A `filter' rule $f_s$, a scaling factor $N_s$ and a set $T_s$ of tuples from the table. The set $T_s$ consists of a $\frac{1}{N_s}$ uniformly sampled fraction of tuples covered by $f_s$. The scaling factor $N_s$ is used to translate the count of a rule on the sample into an estimate of the count over the entire table. The sum of $|T_s|$ over all samples $s$ is not allowed to exceed capacity $M$ at any point. 
% TODO: Give example of what samples we'd keep.

@@

\subsubsection{Algorithms for deciding what to sample}\label{sec:sampling_algorithms}
We now discuss algorithms for the SampleHandler to decide what sizes of Samples to maintain in memory. Briefly, we want to determine sample sizes that maximize the probability that the next user click can be answered using the existing samples, without reading from the Hard Disk.

@@

%TODO: Comment 15 of Aditya. I don't quite understand it. 
When the SamplerHandler uses \textbf{Create} for a rule $r$, it needs to make a pass through the entire table, as well as potentially shrink some existing samples to free up memory. Since making a pass over the the table from the Hard Disk is usually a bottleneck, it can also do things like creating samples for rules other than $r$, and augmenting existing samples, in the same pass. Hence, we assume that in a \textbf{Create} phase, the SampleHandler not only creates one new sample for $r$, but also potentially creates other new samples, or resizes existing samples. For each displayed rule $r^{\prime}$, it may create a new sample for $r^{\prime}$ in the same pass through the table. Based on the current leaves and their expansion probabilities, it finds an optimal set of sizes of samples to create for each displayed rule. More specifically, for every displayed rule $r^{\prime}$, it determines an integer $n_{r^{\prime}}$, and then creates a fresh sample $s_{r^{\prime}}$ with $f_{s_{r^{\prime}}} = r^{\prime}$ and $|T_{s_{r^{\prime}}}| = n_{r^{\prime}}$ while making its pass through the table.

>>>>

\section{Smart Drill-Down Algorithms} \label{sec:algorithms}
We now describe online algorithms for implementing
the smart drill-down operator. We assume in this section that all columns are categorical (so numerical columns have been bucketized beforehand). We further discuss bucketization of numerical attributes in the Extensions section in the technical report~\cite{tr}.

@@

\noindent Problem~\ref{prob:optimal-subrule-list} with parameters $(T, W, k)$ can be reduced to Problem~\ref{prob:optimal-rule-list} as follows:
\begin{enumerate}
\item $[$Rule Drill-Down$]$ If the user clicked on rule $r$ in Problem~\ref{prob:optimal-subrule-list}, then we can conceptually make one pass through the table $T$ to filter for tuples covered by rule $r$, and store them in a temporary table $T_r$. Then, we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W, k)$.
\item $[$Star Drill-Down$]$ If the user clicked on a $\star$ in column $c$ of rule $r$, then we first filter table $T$ to get a smaller table $T_r$ consisting of tuples from $T$ that are covered by $r$. In addition, we change the weight function $W$ from Problem~\ref{prob:optimal-subrule-list} to a weight function $W^{\prime}$ such that : For any rule $r^{\prime}$, $W^{\prime}(r^{\prime}) = 0$ if $r^{\prime}$ has a $\star$ in column $c$, and $W^{\prime}(r^{\prime}) = W(r^{\prime})$ otherwise. Then, we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W^{\prime}, k)$.
\end{enumerate}

As a first step towards solving Problem~\ref{prob:optimal-rule-list}, we show that the rules in the optimal list must effectively be ordered in decreasing order by weight. Note that the weight of a rule is independent of its $MCount$. The $MCount$ of a rule is the number of tuples that have been `assigned' to it, and each tuple assigned to rule $r$ contributes $W(r)$ to the total score. Thus if the rules are not in decreasing order by weight in a rule list $R$, then switching the order of rules in $R$ transfers some tuples from a lower weight rule to a higher weight rule, which can increase total score.

\begin{lemma}\label{lemma:rule-ordering}
Let $R$ be a rule-list. Let $R^{\prime}$ be the rule-list having the same rules as $R$, but ordered in descending order by weight. Then
$$\text{Score}(R^{\prime}) \geq \text{Score}(R)$$
\end{lemma}
The proof of this lemma, as well as other proofs, can be found in the appendix of the technical report~\cite{tr}.

\noindent Thus it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, we can define Score for a \emph{set} of rules as follows:

@@

This gives us a reduced version of Problem~\ref{prob:optimal-rule-list}: 
\begin{problem}\label{prob:optimal-rule-set}
Given a table $T$, a monotonic weight function $W$, and a number $k$, find the set (not list) $R$ of $k$ rules which maximizes Score($R$) as defined in Definition~\ref{def:set-score}.
\end{problem}

@@

\item In order to find the rule $r$ to add in each step, we need to measure the impact on Score for each $r$. This is done in several passes over the table, using ideas from the a-priori algorithm~\cite{apriori} for frequent item-set mining. 
\squishend

In some cases, the dataset may still be too large for us to return a good rule set in
a reasonable time; in such cases, we may want to run our algorithm on a sample of the table
rather than the entire table. In Section~\ref{sec:sampling}, we describe a scheme 
for maintaining multiple samples in memory and using them to improve response 
time for different drill down operations performed by the user. Our sampling scheme dynamically adapts to the current interaction scenario that the user is in; drawing from ideas in approximation algorithms and optimization theory.

\subsection{Greedy Approximation Algorithm}\label{sec:greedy-approx}
\stitle{Submodularity:} We will now show that the Score function over sets of rules has a property called {\em submodularity}, giving us a greedy approximation algorithm for optimizing it. 
\begin{definition}
A function $f: 2^S \rightarrow \mathbb{R}$ for any set $S$ is said to be submodular if and only if, for every $s \in S$, and $A \subset B \subset S$ with $s \notin A$:
$$f(A \cup \left\lbrace s \right\rbrace) - f(A) \geq f(B \cup \left\lbrace s \right\rbrace) - f(B)$$
\end{definition}
Intuitively, this means that the marginal value of adding an element to a set $S$ cannot increase if we add it to a superset of $S$ instead. For monotonic non-negative submodular functions, the problem of finding the set of a given size with maximum value for the function can be found approximately in a greedy fashion.

@@

The parameter $m_w$ stands for \textit{Max Weight}. The parameter $m_w$ tells the algorithm to assume that all rules that get selected in the optimal solution are going to have weight $\leq m_w$. Thus, if $S_o$ denotes set of rules with maximum score, then as long as $m_w \geq \textrm{max}_{r \in S_o}W(r)$, Algorithm~\ref{algo:best-rule-set} is guaranteed to return $S_o$. On the other hand if $m_w < W(r)$ for some $r \in S_o$, then there is a chance that the set returned by Algorithm~\ref{algo:best-rule-set} does not contain $r$. Algorithm~\ref{algo:best-rule-set} runs faster for smaller values of $m_w$, and may only return a suboptimal result if $m_w < \textrm{max}_{r \in S_o}W(r)$. In practice, $\textrm{max}_{r \in S_o}W(r)$ is usually small. This is because as the size (and weight) of a rule increases, its Count falls rapidly. The Count tends to decrease exponentially with rule size, while Weight increases linearly for common weight functions (such as $W(r) = \text{Size}(r)$). Thus, rules with high weight and size have very low count, and are unlikely to occur in the optimal solution set $S_o$. Our experiments in Section~\ref{sec:experiments} also show that the weights of rules in the optimal set tend to be small.

@@

In order to avoid counting too many rules, we use an idea from the {\em a-priori} algorithm for frequent itemset mining~\cite{apriori}. Recall that the a-priori algorithm is used to find all frequent itemsets that have a support greater than a threshold. Unlike the frequent itemset mining algorithm, our goal is to find the single best marginal rule. Since we only aim to find one rule at a time, our pruning power is significantly higher than a vanilla a-priori algorithm, and we terminate in much fewer passes over the dataset. 
We compute the best marginal rule over several passes, with the maximum number of passes equal to the maximum size of a rule. In the $j^{th}$ pass, we compute counts and marginal values for rules of size $j$. To give an example, suppose we had three columns $c_1$, $c_2$, and $c_3$. In the first pass, we would compute the counts and marginal values of all rules of size $1$. In the second pass, instead of finding marginal values for all size $2$ rules, we can use our knowledge of counts from the first pass to upper bound the potential counts and marginal values of size $2$ rules, and be more selective about which rules to count in the second pass. For instance, suppose we know that the rule $(a, \star, \star)$ has a count of $1000$, while $(\star, b, \star)$ has a count of $100$. Then for any value $c$ in column $c_3$ we would know that the count of $(\star, b, c)$ is at most $100$ because it cannot exceed that of $(\star, b, \star)$. This implies that the maximum marginal value of any super-rule of $(\star, b, c)$ having weight $\leq m_w$ is at most $100m_w$. If the rule $(a, \star, \star)$ has a marginal value of $800$, then the marginal value of any super-rule of $(\star, b, \star)$ cannot possibly exceed that of $(a, \star, \star)$. Since our aim is to only find the highest marginal value rule, we can skip counting for all super-rules of $(\star, b, \star)$ for future passes.

@@

Note that the reader may be wondering why we did not simply count the score of each rule using a variant of the a-priori algorithm in one pass, and then pick the set of rules that maximizes score subsequently. This is because doing so will lead to a sub-optimal set of rules: by not accounting for the rules that have already been selected, we will not be able to ascertain the marginal benefit of adding an additional rule correctly.

@@

MarginalValue($R$) $+=$ $W(R) - \text{min}(W(R), W(R_S))$
}
}
$C = C \cup C_n$

$C_o = C_n$

@@

@@

\subsection{Dynamic Sampling for Large Tables}\label{sec:sampling}
We now describe our sampling schemes for improving the running time of our algorithm on tables that are too large to fit in main memory. First in Section~\ref{sec:sample-using}, we motivate the need for sampling. Then we describe a component of our system, called the {\em SampleHandler}, which is responsible for creating and maintaining samples of the table in memory, subject to user specified memory constraints. The SampleHandler maintains multiple samples corresponding to different parts of the table, which can be used depending on which rule the user decides to expand next. Then in Section~\ref{sec:sampling_algorithms}, we describe ways to efficiently allocate memory to different samples, so as to maximize the probability that we can respond to the next user operation without accessing the hard disk. Finally, we mention some additional optimizations we can make, and heuristics for setting the minimum sample size required from the SampleHandler.

@@

At all points, the SampleHandler maintains a set of samples in memory. For instance, it may keep a sample of tuples used to expand the first (trivial) rule, and another sample used to expand the rule last clicked on by the user. Each sample $s$ is an object with three attributes: A `filter' rule $f_s$, a scaling factor $N_s$ and a set $T_s$ of tuples from the table. The set $T_s$ consists of a $\frac{1}{N_s}$ uniformly sampled fraction of tuples covered by $f_s$. The scaling factor $N_s$ is used to translate the count of a rule on the sample into an estimate of the count over the entire table. The sum of $|T_s|$ over all samples $s$ is not allowed to exceed capacity $M$ at any point. 
% TODO: Give example of what samples we'd keep.

@@

\subsubsection{Algorithms for deciding what to sample}\label{sec:sampling_algorithms}
We now discuss algorithms for the SampleHandler to decide what sizes of Samples to maintain in memory. Briefly, we want to determine sample sizes that maximize the probability that the next user click can be answered using the existing samples, without reading from the hard disk.

@@

%TODO: Comment 15 of Aditya. I don't quite understand it. 
When the SamplerHandler uses \textbf{Create} for a rule $r$, it needs to make a pass through the entire table, as well as potentially shrink some existing samples to free up memory. Since making a pass over the the table from the hard disk is usually a bottleneck, it can also do things like creating samples for rules other than $r$, and augmenting existing samples, in the same pass. Hence, we assume that in a \textbf{Create} phase, the SampleHandler not only creates one new sample for $r$, but also potentially creates other new samples, or resizes existing samples. For each displayed rule $r^{\prime}$, it may create a new sample for $r^{\prime}$ in the same pass through the table. Based on the current leaves and their expansion probabilities, it finds an optimal set of sizes of samples to create for each displayed rule. More specifically, for every displayed rule $r^{\prime}$, it determines an integer $n_{r^{\prime}}$, and then creates a fresh sample $s_{r^{\prime}}$ with $f_{s_{r^{\prime}}} = r^{\prime}$ and $|T_{s_{r^{\prime}}}| = n_{r^{\prime}}$ while making its pass through the table.
